---
title: "Historical Data"
execute:
  echo: false
format: 
  html:
    fig-width: 8
    fig-height: 4
    code-fold: false
---

```{r load-pkg, echo = FALSE, message = FALSE}
library (repometrics)
library (lubridate)
```
This page includes several graphs providing insight into the historical
development of the package.

## Data on individual functions

This plot shows time series for the development of the following measures for each function in the package:

- `doclines` = Numbers of lines of documentation per function.
- `npars` = Numbers of parameters per function.
- `loc` = Numbers of lines of code per function.
- `ext_calls` = Numbers calls made to external functions.

The selector below allows any one of these variables to be selected and
plotted. Results in each case are displayed as both median and median values
per function, along with the sum over all functions within the package. These
"sum" values are arbitrarily rescaled for visual display on similar scales to
the other measures.

```{r load-data}
dat <- readRDS ("results.Rds")
```
```{r stats-data}
cols <- names (dat$stats) [which (!names (dat$stats) %in% c ("package", "version"))]
stats <- dat$stats [, cols]
stats$date <- lubridate::ymd (strftime (stats$date, "%y-%m-%d"))
index <- which (stats$measure == "sum")
stats$npars [index] <- stats$npars [index] / 100
stats$loc [index] <- stats$loc [index] / 100
stats$ext_calls [index] <- stats$ext_calls [index] / 20
stats$doclines [index] <- stats$doclines [index] / 20

stats <- tidyr::pivot_longer (stats, c ("doclines", "npars", "loc", "ext_calls"))
```

```{r ojs-in-stats, echo = FALSE}
ojs_define (stats_in = stats)
```
```{ojs stats-transpose-and-filter}
stats = {
    return transpose(stats_in).map(row => ({
        ...row,
        date: new Date(row.date)
    }));
}
viewof name = Inputs.radio(
    ["doclines", "npars", "loc", "ext_calls"],
    {
        value: "npars",
        label: "Variable:",
    }
)
statsFiltered = stats.filter(function(row) {
  return name.includes(row.name)
})
```

```{ojs stats-plot}
Plot.plot({
    style: `
        overflow: visible;
    `,
    marginLeft: 60,
    marginBottom: 50,
    x: {grid: true},
    y: {grid: true},
    marks: [
        Plot.ruleY([0]),
        Plot.lineY(
            statsFiltered,
            {
                x: "date",
                y: "value",
                stroke: "measure",
                fontSize: 18
            }
        ),
        Plot.text(
            statsFiltered,
            Plot.selectLast({
                x: "date",
                y: "value",
                z: "measure",
                text: "measure",
                textAnchor: "start",
                dx: 3,
                fontSize: 18
            })
        ),
        Plot.axisX(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisX(
            {
                fontSize: 20,
                label: "Date",
                labelAnchor: "center",
                labelOffset: 40,
                ticks: []
            }
        ),
        Plot.axisY(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisY(
            {
                fontSize: 24,
                label: "Value",
                labelAnchor: "center",
                labelOffset: 55,
                ticks: []
            }
        ),
    ]
})
```

## General data

This plot shows some general data.

```{r desc-data}
cols <- names (dat$desc_data) [which (!names (dat$desc_data) %in% c ("package"))]
desc <- dat$desc_data [, cols]
desc$date <- lubridate::ymd (strftime (desc$date, "%y-%m-%d"))
desc$base_calls <- desc$base_calls / 10

cols <- names (desc) [which (!names (desc) %in% c ("date"))]
desc <- tidyr::pivot_longer (
    desc,
    c ("n_aut", "n_ctb", "n_fns_tot", "n_fns_exp", "n_ext_pkgs", "base_calls")
)
names (desc) <- c ("date", "desc_variable", "value")
desc$group <- "authors"
desc$group [grep ("^n\\_fns", desc$desc_variable)] <- "functions"
desc$group [desc$desc_variable %in% c ("n_ext_pkgs", "base_calls")] <- "external"
```

```{r ojs-in-desc, echo = FALSE}
ojs_define (desc_in = desc)
```

```{ojs desc-transpose-and-filter}
desc = {
    return transpose(desc_in).map(row => ({
        ...row,
        date: new Date(row.date)
    }));
}
viewof group = Inputs.radio(
    ["authors", "functions", "external"],
    {
        value: "authors",
        label: "Variable Types:",
    }
)
descFiltered = desc.filter(function(row) {
  return group.includes(row.group)
})
```

```{ojs desc-plot}
Plot.plot({
    style: `
        overflow: visible;
    `,
    marginLeft: 60,
    marginBottom: 50,
    x: {grid: true},
    y: {grid: true},
    marks: [
        Plot.ruleY([0]),
        Plot.lineY(
            descFiltered,
            {
                x: "date",
                y: "value",
                stroke: "desc_variable",
                fontSize: 18
            }
        ),
        Plot.text(
            descFiltered,
            Plot.selectLast({
                x: "date",
                y: "value",
                z: "desc_variable",
                text: "desc_variable",
                textAnchor: "start",
                dx: 3,
                fontSize: 18
            })
        ),
        Plot.axisX(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisX(
            {
                fontSize: 20,
                label: "Date",
                labelAnchor: "center",
                labelOffset: 40,
                ticks: []
            }
        ),
        Plot.axisY(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisY(
            {
                fontSize: 24,
                label: "Value",
                labelAnchor: "center",
                labelOffset: 55,
                ticks: []
            }
        ),
    ]
})
```

## Numbers of Files and Lines of Code

```{r loc-data}
rm_cols <- c ("package", "nempty", "nspaces", "nchars", "nexpr", "ntabs", "indentation")
cols <- names (dat$loc) [which (!names (dat$loc) %in% rm_cols)]
loc <- dat$loc [, cols]
loc$date <- lubridate::ymd (strftime (loc$date, "%y-%m-%d"))

loc <- tidyr::pivot_longer (
    loc,
    c ("nfiles", "nlines", "ncode", "ndoc")
) |>
    dplyr::rename (loc_measure = name) |>
    dplyr::mutate (loc_measure = dplyr::case_match (
        loc_measure,
        "nfiles" ~ "files",
        "nlines" ~ "total",
        "ncode" ~ "code",
        "ndoc" ~ "doc"
    ))
loc_files <- loc [loc$loc_measure == "files", ]
loc_lines <- loc [loc$loc_measure != "files", ]
```

```{r ojs-in-loc, echo = FALSE}
ojs_define (loc_files_in = loc_files)
ojs_define (loc_lines_in = loc_lines)
```

This first plot shows total numbers of files in each specified sub-directory.


```{ojs loc_files-transpose}
loc_files = {
    return transpose(loc_files_in).map(row => ({
        ...row,
        date: new Date(row.date)
    }));
}
```


```{ojs loc-files-plot}
Plot.plot({
    style: `
        overflow: visible;
    `,
    marginLeft: 60,
    marginBottom: 50,
    x: {grid: true},
    y: {grid: true},
    marks: [
        Plot.ruleY([0]),
        Plot.lineY(
            loc_files,
            {
                x: "date",
                y: "value",
                stroke: "dir",
                fontSize: 18
            }
        ),
        Plot.text(
            loc_files,
            Plot.selectLast({
                x: "date",
                y: "value",
                z: "dir",
                text: "dir",
                textAnchor: "start",
                dx: 3,
                fontSize: 18
            })
        ),
        Plot.axisX(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisX(
            {
                fontSize: 20,
                label: "Date",
                labelAnchor: "center",
                labelOffset: 40,
                ticks: []
            }
        ),
        Plot.axisY(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisY(
            {
                fontSize: 24,
                label: "Numbers of Files",
                labelAnchor: "center",
                labelOffset: 55,
                ticks: []
            }
        ),
    ]
})
```

This next plot shows numbers of lines, both of code and documentation.

```{ojs loc-lines-transpose-and-filter}
loc_lines = {
    return transpose(loc_lines_in).map(row => ({
        ...row,
        date: new Date(row.date)
    }));
}
viewof loc_measure = Inputs.radio(
    ["total", "code", "doc"],
    {
        value: "total",
        label: "LOC Type:",
    }
)
locLinesFiltered = loc_lines.filter(function(row) {
  return loc_measure.includes(row.loc_measure)
})
```

```{ojs loc-lines-plot}
Plot.plot({
    style: `
        overflow: visible;
    `,
    marginLeft: 80,
    marginBottom: 50,
    x: {grid: true},
y: {grid: true, type: "log"},
    marks: [
        Plot.ruleY([0]),
        Plot.lineY(
            locLinesFiltered,
            {
                x: "date",
                y: "value",
                stroke: "dir",
                fontSize: 18
            }
        ),
        Plot.text(
            locLinesFiltered,
            Plot.selectLast({
                x: "date",
                y: "value",
                z: "dir",
                text: "dir",
                textAnchor: "start",
                dx: 3,
                fontSize: 18
            })
        ),
        Plot.axisX(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisX(
            {
                fontSize: 20,
                label: "Date",
                labelAnchor: "center",
                labelOffset: 40,
                ticks: []
            }
        ),
        Plot.axisY(
            {
                fontSize: 14,
                label: "",
                labelArrow: false
            }
        ),
        Plot.axisY(
            {
                fontSize: 24,
                label: "Numbers of Lines",
                labelAnchor: "center",
                labelOffset: 70,
                ticks: []
            }
        ),
    ]
})
```
