---
title: "CHAOSS metrics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CHAOSS metrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set (
    collapse = TRUE,
    comment = "#>"
)
```

The `repometrics` package collates many metrics of a nominated repository,
including the metrics defined by the [CHAOSS community ("Community Health
Analytics in Open Source Software")](https://chaoss.community/). The metrics
implemented by this package can be seen by first loading the package:

```{r pkgload}
library (repometrics)
```

And the calling this function:

```{r list-metrics, eval = FALSE}
rm_chaoss_metrics_list ()
```

That returns a `data.frame` with two columns, rendered here in hyperlinked
form:

```{r DT-metrics, eval = TRUE, echo = FALSE}
metrics <- rm_chaoss_metrics_list ()
metrics$url <- paste0 (
    '<a target=_blank href="',
    metrics$url,
    '">',
    metrics$url,
    "</a>"
)
# https://datatables.net/reference/option/dom
# full default set: (lftipr)
DT::datatable (metrics, escape = FALSE, options = list (dom = "ltipr"))
```

As noted in the documentation for [the `rm_chaoss_metrics_list`
function](https://docs.ropensci.org/repometrics/reference/rm_chaoss_metrics_list.html):

```{r help-node, echo = FALSE, eval = TRUE, results = "asis"}
db <- tools::Rd_db ("repometrics")
fn <- "rm_chaoss_metrics_list"
fn_help <- db [[paste0 (fn, ".Rd")]]
get_Rd_metadata <- utils::getFromNamespace (".Rd_get_metadata", "tools")
fn_note <- gsub ("\\n+", " ", get_Rd_metadata (fn_help, "note"))
cat (paste0 ("> ", fn_note))
```
